Model_CFU

### 2016-12-07 Projects/HumanCdGF_cdiff_colonization.Rmd
add importance plots

#### Predictive OTUs  
##### OTUs predictive of _Colonization level_:  
`r names(top_features)`

@@

##### OTUs predictive of _Inocula Source_:  
`r names(top_features_src)`

@@

```{r plot colonization otu correlations, fig.width=10, fig.height=18}
subset(cfu_all_shared_df, select = 
       c("log_cfu_med", names(feat_cor_cfu)[feat_cor_cfu>0.5 & feat_cor_cfu < 1])) %>% 
  gather(OTU, abundance, contains('Otu')) %>% 
  ggplot(aes(x = abundance, y = log_cfu_med)) + geom_point() + 
    facet_wrap(~OTU, ncol = 4, scales = 'free_x')
```

>>>>

#### Predictive OTUs  
##### OTUs predictive of _Colonization level_ (Top 10%)

```{r colonization otu importance, fig.width=6, fig.height=6}
top_otus <- get_tax(row_list = names(top_features))$tax_label

data.frame(OTU = factor(top_otus, 
                        levels = top_otus[order(top_features)]), 
           Importance = top_features/max(top_features)) %>% 
  ggplot(aes(x = OTU, y = Importance)) + 
    geom_point() + coord_flip() + 
    labs(y = 'Importance (Relative MDA)', x = NULL) + 
    theme(panel.background = element_rect(linetype = 1, size = 2, fill = 'white', color = 'black'),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.major.y = element_line(colour = "gray", linetype = "dotted"),
          panel.grid.minor.y = element_line(colour = "gray", linetype = "dotted"),
          axis.text.y = element_text(color = c(rep('black', length(top_features)-12),
                                               rep('red', 12)), 
                                     hjust = 0))
```

@@

##### OTUs predictive of _Inocula Source_ (Top 10%)

```{r source otu importance, fig.width=6, fig.height=6}
top_otus_src <- get_tax(row_list = names(top_features_src))$tax_label

data.frame(OTU = factor(top_otus_src, 
                        levels = top_otus_src[order(top_features_src)]), 
           Importance = top_features_src/max(top_features_src)) %>% 
  ggplot(aes(x = OTU, y = Importance)) + 
    geom_point() + coord_flip() + 
    labs(y = 'Importance (Relative MDA)', x = NULL) + 
    theme(panel.background = element_rect(linetype = 1, size = 2, fill = 'white', color = 'black'),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.major.y = element_line(colour = "gray", linetype = "dotted"),
          panel.grid.minor.y = element_line(colour = "gray", linetype = "dotted"),
          axis.text.y = element_text(color = c(rep('black', length(top_features)-12),
                                               rep('red', 12)), 
                                     hjust = 0))
```

@@

```{r plot colonization otu correlations, fig.width=10, fig.height=18}
subset(cfu_all_shared_df, select = 
       c("log_cfu_med", names(head(top_features,12)))) %>% 
  gather(OTU, abundance, contains('Otu')) %>% 
  ggplot(aes(x = abundance, y = log_cfu_med)) + geom_point() + 
    facet_wrap(~OTU, ncol = 4, scales = 'free_x') + scale_x_log10()
```
